As any non-\/trivial software system, Google \mbox{\hyperlink{classMock}{Mock}} has some known limitations and problems. We are working on improving it, and welcome your help! The follow is a list of issues we know about.

\subsection*{R\+E\+A\+D\+ME contains outdated information on Google \mbox{\hyperlink{classMock}{Mock}}\textquotesingle{}s compatibility with other testing frameworks}

The {\ttfamily R\+E\+A\+D\+ME} file in release 1.\+1.\+0 still says that Google \mbox{\hyperlink{classMock}{Mock}} only works with Google Test. Actually, you can configure Google \mbox{\hyperlink{classMock}{Mock}} to work with any testing framework you choose.

\subsection*{Tests failing on machines using Power PC C\+P\+Us (e.\+g. some Macs)}

{\ttfamily \mbox{\hyperlink{namespacegmock__output__test}{gmock\+\_\+output\+\_\+test}}} and {\ttfamily gmock-\/printers\+\_\+test} are known to fail with Power PC C\+P\+Us. This is due to portability issues with these tests, and is not an indication of problems in Google \mbox{\hyperlink{classMock}{Mock}} itself. You can safely ignore them.

\subsection*{Failed to resolve libgtest.\+so.\+0 in tests when built against installed Google Test}

This only applies if you manually built and installed Google Test, and then built a Google \mbox{\hyperlink{classMock}{Mock}} against it (either explicitly, or because gtest-\/config was in your path post-\/install). In this situation, Libtool has a known issue with certain systems\textquotesingle{} ldconfig setup\+:

\href{http://article.gmane.org/gmane.comp.sysutils.automake.general/9025}{\texttt{ http\+://article.\+gmane.\+org/gmane.\+comp.\+sysutils.\+automake.\+general/9025}}

This requires a manual run of \char`\"{}sudo ldconfig\char`\"{} after the \char`\"{}sudo make install\char`\"{} for Google Test before any binaries which link against it can be executed. This isn\textquotesingle{}t a bug in our install, but we should at least have documented it or hacked a work-\/around into our install. We should have one of these solutions in our next release. 